Global phase diagram and possible quantum spin liquid in the triangular $J$-$K$-$\Gamma$ model

### 2020-11-11 paper/paper.tex
Paper 2020-08-17 21:53

In this paper, we study the global phase diagram and the phase transitions of the triangular lattice $J$-$K$-$\Gamma$ model using a combination of ED and classical analyses. We find that the ED results are basically consistent with the classical analyses such as the classical Monte Carlo simulations. In the HK limit ($\Gamma=0$), there are five classical phases: one FM, two stripe, one $120^{\circ}$ N\'{e}el and its dual phases. For the pure AFM Kitaev model, although the system has highly degenerate classical GSs composed of the stripe and nematic states, the order-by-disorder mechanism caused by quantum fluctuations makes the system select the stripe state to be the GS. When the $\Gamma$ term is included, we find five new phases: two FM, one stripe, one modulated stripe and one possible QSL phases. With the aid of classical analysis, we determine the spin directions for each magnetically ordered phase and explain that why there are phase transitions between the phases with the same type of classical orders. On the other hand, we find that the order-by-disorder mechanism makes the GSs of the pure $\Gamma$ models have FM orders, although the classical analyses suggest that the GSs are highly degenerate. For the possible QSL phase, based on the investigation of the spin excitation spectrum, we find that the GS is probably a gapped $Z_{2}$ QSL.

@@

\begin{figure*}
    \centering
    \includegraphics[width=0.95\textwidth]{fig/QuantumGlobalPhaseDiagram.pdf}
    \caption{\label{fig:QuantumPhaseDiagram}(Color online) Global phase diagram of the triangular lattice $J$-$K$-$\Gamma$ model. The angle $\alpha$ and $\beta$ denote the radial and azimuthal angles, respectively. There are in total ten phases including three FM phases denoted as FM-A, FM-B and FM-C, three stripe phases designated as Stripe-A, Stripe-B and Stripe-C, a modulated stripe phase, a 120$^\circ$ N\'{e}el phase, a dual N\'{e}el phase and a possible QSL phase. Phase boundaries are determined by the singularities of $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ from ED calculations except for that depicted by the dashed line between the modulated stripe and stripe-B phases given by the classical analyses. The inset sub-figure(a) is the global phase diagram of the HK model. The two-way arrows indicate parameter pairs that can be connected by the FST.}
\end{figure*}

The quantum phase diagrams obtained by the ED method for $\Gamma \geq 0$ and $\Gamma \leq 0$ on a $4 \times 6$ cluster with the periodic boundary condition are presented in Fig.~\ref{fig:QuantumPhaseDiagram}. The phase boundaries are determined by the location of singularities in $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ (see Appendix \ref{apx:PhaseBoundary} for details).

In the HK limit ($\Gamma=0$), as with the previous study~\cite{KaiLi2015}, we find five quantum phases. For pure Heisenberg models ($K=\Gamma=0$), the GSs are well known, i.e., a FM state for $J<0$ and a 120$^\circ$ N\'{e}el state for $J>0$, respectively. As mentioned in Sec.~\ref{sec:Model}, the HK model ($\Gamma=0$) preserves its form under the FST~\cite{PhysRevB.89.014414} but with different exchange interactions. Thus, by virtue of the FST, two more magnetic ordered phases can be identified. For the FM Heisenberg model of the rotated spin operators $\bm{S}^{\prime}$ whose GS is a FM state, the FST maps it to a Heisenberg-Kitaev model of the original spin operators $\bm{S}$ with $\beta=\pi - \arctan\frac{1}{2}$. Accordingly, the FM state of $\bm{S}^{\prime}$ is transformed to a collinear stripe state of $\bm{S}$. Similarly, the AFM Heisenberg model of $\bm{S}^{\prime}$ is also mapped to a Heisenberg-Kitaev model of $\bm{S}$ with $\beta=-\arctan\frac{1}{2}$ and the 120$^\circ$ N\'{e}el state of $\bm{S}^{\prime}$ is transformed to a noncollinear spiral order (Dual N\'{e}el) of $\bm{S}$. However, for the phase containing the AFM Kitaev point ($J=\Gamma=0$, $K=1$), since it is mapped to itself under FST, we can not identify its magnetic properties with the FST.

@@

The properties of each quantum phases, especially the spin configuration of the ordered phases, can be inferred from the SSF defined in Eq.~\eqref{eq:SSF}, so we calculate the SSF for the case of pure AFM Kitaev limit ($J=\Gamma=0$, $K=1$) and present the result in Fig.~\ref{fig:StructureFactors}(a). We find that the SSF shows obvious peaks at the $\tilde{M}$ points, which is a typical characteristic of the stripe order as shown in Fig.~\ref{fig:StructureFactors}(i). For the sake of clarity, we further perform a ``basin-hopping" global optimization~\cite{jp970984n} on a $12 \times 12$ lattice by taking the spins as classical magnetic moments to search for the possible spin configurations under this set of interaction parameters. The stripe orders are indeed possible GS spin configurations, but there are also many nematic states with the same energy as it at the classical level since the AFM chains are decoupled (see Appendix~\ref{apx:DegeneratedStates} for details). When we consider the quantum fluctuations generated by the Kitaev interactions not along the AFM chains, the $4^{th}$ order corrections will give an effective coupling between the next-nearest-neighbor spins~\cite{PhysRevB.92.184416}, which can stabilize the stripe order. Thus, the degeneracy of the spin configurations is lifted by the order-by-disorder mechanism, and we can identify that the phase containing the AFM Kitaev point of the HK model is a stripe phase, which we label the stripe-C in Fig.~\ref{fig:QuantumPhaseDiagram}. Moreover, every stripe order in this phase can be transformed to another degenerate stripe pattern in the same phase by a FST, so these stripe orders are consistent with the FST.

When the $\Gamma$ term is included, we find that the FM phase and the stripe-C phase in the HK model are actually phase boundaries in the global phase diagram of the $J$-$K$-$\Gamma$ model. Moreover, except the 120$^\circ$ N\'{e}el state and the dual N\'{e}el state, which already exist in the HK limit, there are five other new phases according to the singularities of $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$.

To reveal the natures of these new phases, we further study the SSFs in these new phases. Since the stripe phase for $K<0$ in the HK limit is located inside a phase of the global phase diagram, we infer this phase to have a stripe order and denote it as the stripe-A phase in Fig.~\ref{fig:QuantumPhaseDiagram}. To confirm this, we present the SSFs for two typical points, i.e. $\alpha=0.3\pi$, $\beta=0.75\pi$ and $\alpha=0.75\pi$, $\beta=0.25\pi$, in the $\Gamma>0$ and $\Gamma<0$ regions in Fig.~\ref{fig:StructureFactors}(b) and (c), respectively. Both of the SSFs show obvious peaks at the $\tilde{M}$ points, which is a signature feature of the stripe phase. In Fig.~\ref{fig:StructureFactors}(d), we illustrate the SSF for $\alpha=0.3\pi$, $\beta=0$, which also shows distinct peaks at the $\tilde{M}$ points, so the phase containing this point is also a stripe phase and we denote it the stripe-B in the phase diagram.

When we carefully examine the SSF near $\beta=0.5\pi$, we find that the SSF is obviously different from those of the stripe phases. As shown in Fig.~\ref{fig:StructureFactors}(e) for $\alpha=0.3\pi$ and $\beta=0.5\pi$, besides the peaks at the $\tilde{M}$ points, the SSF also shows significant intensities along the boundary of the BZ. In order to clarify whether there is another magnetic ordering phase near $\beta=0.5\pi$, we use the ``basin-hopping" technique again to search for the possible spin order for $\alpha=0.3\pi$ and $\beta=0.5\pi$ on a $12 \times 12$ lattice. The spin configuration is depicted in Fig.~\ref{fig:ModulatedStripe}(a), which exhibits a modulated stripe order. For this modulated stripe order, the spins are ferromagnetic along a next-nearest-neighbor direction and the spin orientation of the ferromagnetic chains are modulated to form a structure with a period of six. As illustrated in Fig.~\ref{fig:ModulatedStripe}(b), the SSF of this classical six-chain stripe order shows clear peaks at the $\tilde{K}$ points in addition to those at the $\tilde{M}$ points, which is consistent with the characteristic of the SSF in Fig.~\ref{fig:StructureFactors}(e) calculated by the ED. We further perform a classical Monte Carlo simulations (see Sec.~\ref{subsec:MethodMC}) on a $24 \times24$ lattice to check the stability of the modulated stripe order in the large-size systems, and the ground-state spin configuration is shown in Fig.~\ref{fig:ModulatedStripe}(c). We find that the spin arrangement is still a modulated stripe order, but the spin orientations are also modulated along the ferromagnetic chains in addition to a larger modulated period perpendicular to the chains. Thus, we divide a transition region between the stipe-A and stripe-B phase and term it the modulated stripe order phase.

For the other two phases with large areas and mainly located in the $J<0$ region of the phase diagram, we show the SSFs of two representative points with $\alpha=0.3\pi, \beta=1.3\pi$ and $\alpha=0.7\pi, \beta=1.65\pi$ in Fig.~\ref{fig:StructureFactors}(f) and (g), respectively. Since the SSFs are peaked at $\tilde{\Gamma}$ point of the first BZ, so both phases have ferromagnetic orders and they are denoted with FM-A and FM-C in Fig.~\ref{fig:QuantumPhaseDiagram}. We note that there are two special points with $\Gamma=\pm1$ ($J=K=0$) in the two FM phases, which are located at the phase boundary in the classical phase diagram~\cite{PhysRevB.92.165108}. Thus, it is worthy to discuss the properties of the pure $\Gamma$ models in details, and we perform the numerical simulations by using the ``basin-hopping" global optimization and classical Monte Carlo methods. For $\Gamma=+1$, apart from the FM GS with the spin orientation lying in the lattice plane, we also found disordered states having the same energy as the FM state. For $\Gamma=-1$, in addition to the FM order perpendicular to the lattice plane, other long-range ordered states which are energetically degenerate with the FM state also appear (see Appendix~\ref{apx:DegeneratedStates} for details). However, for the quantum model, quantum flucations select the FM ordered states as the GS out of the degenerate manifolds of classical states according to our ED calculations. This selection of states among the degenerate classical ground states is the so the called order-by-disorder mechanism, which has previously been applied in a number of insulating magnets, especially in cases where frustration leads to a degenerate manifold of classical ground state configurations that is broken by quantum fluctuations~\cite{JPSJ.54.4494,PhysRevLett.62.2056,PhysRevLett.88.067203,PhysRevB.81.214419,PhysRevLett.109.077204}.
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{fig/StructureFactors.pdf}
    \caption{\label{fig:StructureFactors}(Color online) (a)-(h) Representative SSFs from the ED calculations for different interaction parameters. The green dashed lines marks the first BZ corresponding to the triangular lattice. (i) Characteristic wave vectors for the FM and stipe phases. See Appendix~\ref{apx:SSF} for the SSFs of the 120$^\circ$ N\'{e}el phase, dual N\'{e}el phase and pure $\Gamma$ models.}
\end{figure}

@@

To have a better understanding of the phase transitions between these FM phases, we first study the classical $J$-$K$-$\Gamma$ model where the spin operators are viewed as unit-vectors in the three dimension. For classical FM states, all spins are aligned in parallel and the energy per lattice site is given by
\begin{equation}
    E_{FM}^{c} = (3J + K) + 2 \Gamma (v^x v^y + v^y v^z + v^z v^x) \label{eq:EcFM}
\end{equation}
where $v^x$, $v^y$, $v^z$ are the three components of the classical moment vector. On this level, the moment direction of the FM state is determined solely by $\Gamma$, so the problem becomes finding the global minimum and maximum of the multi-variable function $f(v^x, v^y, v^z) = v^x v^y + v^y v^z + v^z v^x$ with the constraint $|\bm{v}| = 1$. $f(v^x, v^y, v^z)$ takes the maximum value $f_{max}=1$ at $v^x=v^y=v^z=\pm 1/\sqrt{3}$ and minimum value $f_{min}=-0.5$ when the conditions $v^x + v^y + v^z = 0$ and $|\bm{v}| = 1$ are fulfilled. The condition $v^x + v^y + v^z = 0$ specifies a plane perpendicular to the $[111]$ direction, and considering the reference frame shown in Fig.~\ref{fig:ModelDefinition}(b) it is actually the plane of the triangular lattice. That is to say, for $\Gamma > 0$ the ordered moment of the classical FM state prefers to lie in the lattice plane, while for $\Gamma<0$ the ordered moment would perpendicular to the lattice plane. This is the reason that there is a phase transition between the FM-A and FM-C phases, since the dependence of the ground state energy on the interaction parameters is different for the two FM phases, and the phase boundary is the line with $\Gamma=0$.

The classical analysis suggests that the main difference between these FM phases lies in the ordered moment direction. To further confirm this, we use the spin coherent state to extract the moment direction of these FM phases from our ED cluster GS~\cite{PhysRevB.94.064435}. Since the cluster spin coherent state defined in Eq.~(\ref{eq:Spin-1/2CoherentState}) is captured only by a single pair of $(\theta, \phi)$ for the collinear states, it is easy to determine the direction of the FM orders by inspecting the probability map $P(\theta, \phi) = | \langle \Psi (\theta, \phi) | GS \rangle |^2$. The resulting probability maps for two representative interaction parameters of FM-A and FM-C phases are shown in Fig.~\ref{fig:Proabilities}(a) and (b), where the large overlap between the exact cluster GS and FM cluster spin coherent state again provides solid evidence that the corresponding areas are FM phases. For the FM-A phase, the probability map reveals the moment being constrained to the lattice plane (marked by the green dashed line in Fig.~\ref{fig:Proabilities}(a)) with all directions degenerate. The probability map for the FM-C phase is clearly peaked at the direction perpendicular to the lattice plane (marked by the green solid circle in Fig. \ref{fig:Proabilities}(b)). Thus, the moment directions extracted from the ED cluster GS are consistent with the classical analysis. In the HK limit, for the pure FM Heisenberg model ($J=-1$), the FM state is spin rotational invariant and the ordered moment can point any direction. The Kitaev interaction breaks the spin rotational symmetry and pins the orderings to the axis direction (i.e., $x$, $y$ and $z$ directions) when the quantum fluctuations are included, although the classical energy in Eq.~(\ref{eq:EcFM}) is independent of the moment direction (see Appendix~\ref{apx:LSWOfFMA} for details). When the $\Gamma$ interactions are introduced, positive $\Gamma$ couplings drive the ordered moment to the lattice plane and negative $\Gamma$ couplings pin the ordered moment to be perpendicular to the lattice plane. Therefore, the line with $\Gamma=0$ is the phase boundary of the FM-A and FM-C phases.

@@

In the HK limit, for $K>0$, it can be clearly seen from Eq.~\eqref{eq:EcStripeX} that $E_{stripe-x}^{c}$ takes minimum value at $v^x = 0$ which means that stripe-$x$ prefers to lie in the $yz$ plane. An infinitesimal positive $\Gamma$ would fix the ordered moment to the $\bm{v}_0$ direction, whereas the negative $\Gamma$ drives it to the $\bm{v}_1$ direction. Thus, there is a phase transition between the stripe-A and stripe-B phases, as the ground state energies have different dependence on the interaction parameters for the two stripe phases, and the phase boundary is the line with $\Gamma=0$.

>>>>

In this paper, we study the global phase diagram and the phase transitions of the triangular lattice $J$-$K$-$\Gamma$ model in detail using a combination of ED and classical analyses. We find that the ED results are basically consistent with the classical analyses such as the classical Monte Carlo simulations. In the HK limit ($\Gamma=0$), there are five classical phases: one FM, two stripe, one $120^{\circ}$ N\'{e}el and its dual phases. For the pure AFM Kitaev model, although the system has highly degenerate classical GSs composed of the stripe and nematic states, the order-by-disorder mechanism caused by quantum fluctuations makes the system select the stripe state to be the GS. When the $\Gamma$ term is included, we find five new phases: two FM, one stripe, one modulated stripe and one possible QSL phases. With the aid of classical analysis, we determine the spin directions for each magnetically ordered phase and explain that why there are phase transitions between the phases with the same type of classical orders. On the other hand, we find that the order-by-disorder mechanism makes the GSs of the pure $\Gamma$ models have FM orders, although the classical analyses suggest that the GSs are highly degenerate. For the possible QSL phase, based on the investigation of the spin excitation spectrum, we find that the GS is probably a gapped $Z_{2}$ QSL.

@@

\begin{figure*}
    \centering
    \includegraphics[width=0.95\textwidth]{fig/QuantumGlobalPhaseDiagram.pdf}
    \caption{\label{fig:QuantumPhaseDiagram}(Color online) Global phase diagram of the triangular lattice $J$-$K$-$\Gamma$ model. The angle $\alpha$ and $\beta$ denote the radial and azimuthal angles, respectively. There are in total ten phases including three FM phases denoted as FM-A, FM-B and FM-C, three stripe phases designated as Stripe-A, Stripe-B and Stripe-C, a modulated stripe phase, a 120$^\circ$ N\'{e}el phase, a dual N\'{e}el phase and a possible QSL phase. Phase boundaries are determined by the singularities of $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ from ED calculations except for that depicted by the dashed line between the modulated stripe and stripe-B phases given by the classical analyses.}
\end{figure*}

The quantum phase diagrams obtained by the ED method for $\Gamma \geq 0$ and $\Gamma \leq 0$ on a $4 \times 6$ cluster with the periodic boundary condition are presented in Fig.~\ref{fig:QuantumPhaseDiagram}, where the phase boundaries are determined by the location of singularities in $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ (see Appendix \ref{apx:PhaseBoundary} for details). We find nine magnetically ordered phases and a possible QSL phase. The nine ordered magnetic phases consist of three stripe phases (dubbed as stripe-A, strip-B and stripe-C in Fig.~\ref{fig:QuantumPhaseDiagram}), three ferromagnetic phases (dubbed as FM-A, FM-B and FM-C in Fig.~\ref{fig:QuantumPhaseDiagram}), one 120$^\circ$ N\'{e}el phase, one dual N\'{e}el phase and one modulated stripe phase. In the followings, we will discuss the details on the natures of these phases and the corresponding phase transitions.

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{fig/HKModel.pdf}
    \caption{\label{fig:HKModel}(Color online) Phase diagram in the HK limit ($\Gamma=0$). The double-arrow lines are the representative lines that connect the points exactly related by the FST.}
\end{figure}
Let's first discuss the the HK limit for $\Gamma=0$. As with the previous study~\cite{KaiLi2015}, we find five quantum phases (see Fig.~\ref{fig:HKModel}). For pure Heisenberg models ($K=\Gamma=0$), the GSs are well known, i.e., a FM state (denoted as FM-A) for $J<0$ and a 120$^\circ$ N\'{e}el state for $J>0$, respectively. As mentioned in Sec.~\ref{sec:Model}, the HK model ($\Gamma=0$) preserves its form under the FST~\cite{PhysRevB.89.014414} but with different exchange interactions. Thus, by virtue of the FST, we can identify other two magnetically ordered phases. For the FM Heisenberg model of the rotated spin operators $\bm{S}^{\prime}$ whose GS is a FM state, the FST maps it to a Heisenberg-Kitaev model of the original spin operators $\bm{S}$ with $\beta=\pi - \arctan\frac{1}{2}$. Accordingly, the FM state of $\bm{S}^{\prime}$ is transformed to a collinear stripe state (denoted as stripe-A) of $\bm{S}$. Similarly, the AFM Heisenberg model of $\bm{S}^{\prime}$ is also mapped to a Heisenberg-Kitaev model of $\bm{S}$ with $\beta=-\arctan\frac{1}{2}$, and the 120$^\circ$ N\'{e}el state of $\bm{S}^{\prime}$ is transformed to a noncollinear spiral order (Dual N\'{e}el) of $\bm{S}$. Moreover, as indicated in Fig.~\ref{fig:HKModel}, the transition points $\beta=0.23\pi$ and $0.64\pi$ can also be well mapped to the transition points $\beta=1.90\pi$ and $1.82\pi$ through the FST. The isolated transition point $\beta=\pi$ is also consistent with the FST, as it is mapped to itself under the FST.

For the phase near the AFM Kitaev point ($J=\Gamma=0$, $K=1$), which is between $\beta=1.90\pi$ and $0.23\pi$,  the points in this phase are still mapped to those in the same phase under the FST, so we can not identify its magnetic properties by the FST, and it was supposed to be a magnetically disordered phase in our previous study~\cite{KaiLi2015}. However, as shown in Fig.~\ref{fig:StructureFactors}(a), when we check the SSF in this phase, we find that the SSF shows obvious peaks at the $\tilde{M}$ points, which implies that it is likely to be a magnetically ordered phase. To find out, we further perform a ``basin-hopping" global optimization~\cite{jp970984n} on a $12 \times 12$ lattice by taking the spins as classical magnetic moments to search for the possible spin configurations under this set of interaction parameters. We find that there are two types of degenerate classical GSs, one of which has the stripe order and the other is the nematic state, since the AFM chains are decoupled (see Appendix~\ref{apx:DegeneratedStates} for details). When we consider the quantum fluctuations generated by the Kitaev interactions not along the AFM chains, the $4^{th}$ order corrections will give an effective coupling between the next-nearest-neighbor spins~\cite{PhysRevB.92.184416}, which can stabilize the stripe order. As shown in Fig.~\ref{fig:StructureFactors}(i), the peaks of SSF of the classical stripe orders are also consistent with the result calculated from ED [see Fig.~\ref{fig:StructureFactors}(a)]. Thus, the degeneracy of the spin configurations is lifted by the order-by-disorder mechanism, and we can identify that the phase containing the AFM Kitaev point of the HK model is a stripe phase, which we label the stripe-B. Moreover, every stripe order in this phase (see Appendix~\ref{apx:DegeneratedStates} for details) can be transformed to another degenerate stripe pattern in the same phase by a FST, so these stripe orders are consistent with the FST.

%The stripe orders are indeed possible GS spin configurations, but there are also many nematic states with the same energy as it at the classical level since the AFM chains are decoupled (see Appendix~\ref{apx:DegeneratedStates} for details). When we consider the quantum fluctuations generated by the Kitaev interactions not along the AFM chains, the $4^{th}$ order corrections will give an effective coupling between the next-nearest-neighbor spins~\cite{PhysRevB.92.184416}, which can stabilize the stripe order. Thus, the degeneracy of the spin configurations is lifted by the order-by-disorder mechanism, and we can identify that the phase containing the AFM Kitaev point of the HK model is a stripe phase, which we label the stripe-C in Fig.~\ref{fig:QuantumPhaseDiagram}. Moreover, every stripe order in this phase can be transformed to another degenerate stripe pattern in the same phase by a FST, so these stripe orders are consistent with the FST.

%However, we can not identify the magnetic properties of the phase containing the AFM Kitaev point ($J=\Gamma=0$, $K=1$), since the points in this phase are still mapped to the points in the same phase under the FST.

@@

%The properties of each quantum phases, especially the spin configuration of the ordered phases, can be inferred from the SSF defined in Eq.~\eqref{eq:SSF}, so we calculate the SSF for the case of pure AFM Kitaev limit ($J=\Gamma=0$, $K=1$) and present the result in Fig.~\ref{fig:StructureFactors}(a). We find that the SSF shows obvious peaks at the $\tilde{M}$ points, which is a typical characteristic of the stripe order as shown in Fig.~\ref{fig:StructureFactors}(i).

Next, we will discuss the effects of the $\Gamma$ term on the phase diagram. A natural conjecture is that the phases in the HK limit ($\Gamma=0$) would extend to a larger region in the global phase diagram of the $J$-$K$-$\Gamma$ model. Our ED results do show that the stripe-A phase can extend to a large region from $\Gamma>0$ to $\Gamma<0$, which is consistent with the previous classical results~\cite{PhysRevB.92.165108}. The region of the dual N\'{e}el phase that was dubbed as a dual-$Z_{2}$ vortex crystal phase in Ref.~\onlinecite{PhysRevB.92.165108} is also consistent with the classical results. However, we find that an infinitesimal $\Gamma$ interaction can make the FM-A phase and the stripe-B phase unstable, so these two phases are actually phase boundaries in the global phase diagram. On the other hand, although the the 120$^\circ$ N\'{e}el phase can also extend to a certain region, its area in the phase diagram is much smaller than the classical results~\cite{PhysRevB.92.165108}. Besides these phases that already exist in the HK limit, there are five other new phases according to our ED calculations. Since the SSF is a key physical quantity to reveal the nature of each quantum phases, especially the spin configuration of the ordered phases, we will discuss the properties of the phases with $\Gamma\neq0$ in detail according to the SSFs.

In Fig.~\ref{fig:StructureFactors}(b) and (c), we show the SSFs for two typical points in the stripe-A phase, i.e. $\alpha=0.3\pi$, $\beta=0.75\pi$ and $\alpha=0.75\pi$, $\beta=0.25\pi$ in the $\Gamma>0$ and $\Gamma<0$ regions, respectively. Both of the SSFs show obvious peaks at the $\tilde{M}$ points, which is a typical characteristic of the stripe order as shown in Fig.~\ref{fig:StructureFactors}(i). Thus, this further confirms that the stripe-A phase extents to a large region in the phase diagram. In Fig.~\ref{fig:StructureFactors}(d), we illustrate the SSF for $\alpha=0.3\pi$, $\beta=0$ in a new phase that does not exist in the HK limit, which also shows distinct peaks at the $\tilde{M}$ points, so the phase containing this point is also a stripe phase and we denote it the stripe-C phase in the phase diagram.

%To reveal the natures of these new phases, we further study the SSFs in these new phases. Since the stripe phase for $K<0$ in the HK limit is located inside a phase of the global phase diagram, we infer this phase to have a stripe order and denote it as the stripe-A phase in Fig.~\ref{fig:QuantumPhaseDiagram}. To confirm this, we present the SSFs for two typical points, i.e. $\alpha=0.3\pi$, $\beta=0.75\pi$ and $\alpha=0.75\pi$, $\beta=0.25\pi$, in the $\Gamma>0$ and $\Gamma<0$ regions in Fig.~\ref{fig:StructureFactors}(b) and (c), respectively. Both of the SSFs show obvious peaks at the $\tilde{M}$ points, which is a signature feature of the stripe phase. In Fig.~\ref{fig:StructureFactors}(d), we illustrate the SSF for $\alpha=0.3\pi$, $\beta=0$, which also shows distinct peaks at the $\tilde{M}$ points, so the phase containing this point is also a stripe phase and we denote it the stripe-B in the phase diagram.

When we carefully examine the SSF near $\beta=0.5\pi$, we find that the SSF is obviously different from those of the stripe phases. As shown in Fig.~\ref{fig:StructureFactors}(e) for $\alpha=0.3\pi$ and $\beta=0.5\pi$, besides the peaks at the $\tilde{M}$ points, the SSF also shows significant intensities along the boundary of the BZ. In order to clarify whether there is another magnetic ordering phase near $\beta=0.5\pi$, we use the ``basin-hopping" technique again to search for the possible spin order for $\alpha=0.3\pi$ and $\beta=0.5\pi$ on a $12 \times 12$ lattice. The spin configuration is depicted in Fig.~\ref{fig:ModulatedStripe}(a), which exhibits a modulated stripe order. For this modulated stripe order, the spins are ferromagnetic along a next-nearest-neighbor direction and the spin orientation of the ferromagnetic chains are modulated to form a structure with a period of six. As illustrated in Fig.~\ref{fig:ModulatedStripe}(b), the SSF of this classical six-chain stripe order shows clear peaks at the $\tilde{K}$ points in addition to those at the $\tilde{M}$ points, which is consistent with the characteristic of the SSF in Fig.~\ref{fig:StructureFactors}(e) calculated by the ED. We further perform a classical Monte Carlo simulations (see Sec.~\ref{subsec:MethodMC}) on a $24 \times24$ lattice to check the stability of the modulated stripe order in the large-size systems, and the ground-state spin configuration is shown in Fig.~\ref{fig:ModulatedStripe}(c). We find that the spin arrangement is still a modulated stripe order, but the spin orientations are also modulated along the ferromagnetic chains in addition to a larger modulated period perpendicular to the chains. Thus, we divide a transition region between the stipe-A and stripe-C phase and term it the modulated stripe order phase.

For the other two phases with large areas and mainly located in the $J<0$ region of the phase diagram, we show the SSFs of two representative points with $\alpha=0.3\pi, \beta=1.3\pi$ and $\alpha=0.7\pi, \beta=1.65\pi$ in Fig.~\ref{fig:StructureFactors}(f) and (g), respectively. Since the SSFs are peaked at $\tilde{\Gamma}$ point of the first BZ, so both phases have ferromagnetic orders and they are denoted with FM-B and FM-C in Fig.~\ref{fig:QuantumPhaseDiagram}. We note that there are two special points with $\Gamma=\pm1$ ($J=K=0$) in the two FM phases, which are located at the phase boundary in the classical phase diagram~\cite{PhysRevB.92.165108}. Thus, it is worthy to discuss the properties of the pure $\Gamma$ models in details, and we perform the numerical simulations by using the ``basin-hopping" global optimization and classical Monte Carlo methods. For $\Gamma=+1$, apart from the FM GS with the spin orientation lying in the lattice plane, we also found disordered states having the same energy as the FM state. For $\Gamma=-1$, in addition to the FM order perpendicular to the lattice plane, other long-range ordered states which are energetically degenerate with the FM state also appear (see Appendix~\ref{apx:DegeneratedStates} for details). However, for the quantum model, quantum flucations select the FM ordered states as the GS out of the degenerate manifolds of classical states according to our ED calculations. This selection of states among the degenerate classical ground states is the so the called order-by-disorder mechanism, which has previously been applied in a number of insulating magnets, especially in cases where frustration leads to a degenerate manifold of classical ground state configurations that is broken by quantum fluctuations~\cite{JPSJ.54.4494,PhysRevLett.62.2056,PhysRevLett.88.067203,PhysRevB.81.214419,PhysRevLett.109.077204}.
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{fig/StructureFactors.pdf}
    \caption{\label{fig:StructureFactors}(Color online) (a)-(h) Representative SSFs from the ED calculations for different interaction parameters. The green dashed lines marks the first BZ corresponding to the triangular lattice. (i) Characteristic wave vectors for the FM and stipe phases. See Appendix~\ref{apx:SSF} for the SSFs of the 120$^\circ$ N\'{e}el phase, dual N\'{e}el phase and pure $\Gamma$ models.}
\end{figure}

@@

To have a better understanding of the phase transitions between these FM phases, we first study the classical $J$-$K$-$\Gamma$ model where the spin operators are viewed as unit-vectors in the three dimension. For classical FM states, all spins are aligned in parallel and the energy per lattice site is given by
\begin{equation}
    E_{FM}^{c} = (3J + K) + 2 \Gamma (v^x v^y + v^y v^z + v^z v^x) \label{eq:EcFM}
\end{equation}
where $v^x$, $v^y$, $v^z$ are the three components of the classical moment vector. On this level, the moment direction of the FM state is determined solely by $\Gamma$, so the problem becomes finding the global minimum and maximum of the multi-variable function $f(v^x, v^y, v^z) = v^x v^y + v^y v^z + v^z v^x$ with the constraint $|\bm{v}| = 1$. $f(v^x, v^y, v^z)$ takes the maximum value $f_{max}=1$ at $v^x=v^y=v^z=\pm 1/\sqrt{3}$ and minimum value $f_{min}=-0.5$ when the conditions $v^x + v^y + v^z = 0$ and $|\bm{v}| = 1$ are fulfilled. The condition $v^x + v^y + v^z = 0$ specifies a plane perpendicular to the $[111]$ direction, and considering the reference frame shown in Fig.~\ref{fig:ModelDefinition}(b) it is actually the plane of the triangular lattice. That is to say, for $\Gamma > 0$ the ordered moment of the classical FM state prefers to lie in the lattice plane, while for $\Gamma<0$ the ordered moment would perpendicular to the lattice plane. This is the reason that there is a phase transition between the FM-B and FM-C phases, since the dependence of the ground state energy on the interaction parameters is different for the two FM phases, and the phase boundary is the line with $\Gamma=0$.

In order to confirm the consistency between the above classical analyses and the ED results, we use the spin coherent state to extract the moment direction of these FM phases from our ED cluster GS~\cite{PhysRevB.94.064435}. Since the cluster spin coherent state defined in Eq.~(\ref{eq:Spin-1/2CoherentState}) is captured only by a single pair of $(\theta, \phi)$ for the collinear states, it is easy to determine the direction of the FM orders by inspecting the probability map $P(\theta, \phi) = | \langle \Psi (\theta, \phi) | GS \rangle |^2$. As shown in Fig.~\ref{fig:Proabilities}(a), for the FM-B phase, the peaks of the probability form a ring, which indicates that the moment being constrained to a plane with all directions degenerate. To compare with the classical results, we plot the classical magnetic moment directions with the green dashed line in Fig.~\ref{fig:Proabilities}(a), and we find that the the probability is concentrated near the classical magnetic moment directions. For the FM-C phase, the probability map is clearly peaked at specific directions, which are also consistent with the classical results marked by the green solid circle in Fig. \ref{fig:Proabilities}(b). Moreover, the large overlaps between the exact cluster GSs and FM cluster spin coherent states again provide solid evidences that the ED results are consistent with the classical analyses.

%{\color{red}In the HK limit, for the pure FM Heisenberg model ($J=-1$), the FM state is spin rotational invariant and the ordered moment can point any direction. The Kitaev interaction breaks the spin rotational symmetry and pins the orderings to the axis direction (i.e., $x$, $y$ and $z$ directions) when the quantum fluctuations are included, although the classical energy in Eq.~(\ref{eq:EcFM}) is independent of the moment direction (see Appendix~\ref{apx:LSWOfFMA} for details). When the $\Gamma$ interactions are introduced, positive $\Gamma$ couplings drive the ordered moment to the lattice plane and negative $\Gamma$ couplings pin the ordered moment to be perpendicular to the lattice plane. Therefore, the line with $\Gamma=0$ is the phase boundary of the FM-A and FM-C phases.}

%The resulting probability maps for two representative interaction parameters of FM-B and FM-C phases are shown in Fig.~\ref{fig:Proabilities}(a) and (b), form which we can see that both of the probabilities are concentrated near the classical magnetic moment directions. This large overlap between the exact cluster GS and FM cluster spin coherent state again provides solid evidence that the corresponding regions are FM phases. For the FM-B phase, the probability map reveals the moment being constrained to the lattice plane (marked by the green dashed line in Fig.~\ref{fig:Proabilities}(a)) with all directions degenerate.

@@

In the HK limit, for $K>0$, it can be clearly seen from Eq.~\eqref{eq:EcStripeX} that $E_{stripe-x}^{c}$ takes minimum value at $v^x = 0$ which means that stripe-$x$ prefers to lie in the $yz$ plane. An infinitesimal positive $\Gamma$ would fix the ordered moment to the $\bm{v}_0$ direction, whereas the negative $\Gamma$ drives it to the $\bm{v}_1$ direction. Thus, there is a phase transition between the stripe-A and stripe-C phases, as the ground state energies have different dependence on the interaction parameters for the two stripe phases, and the phase boundary is the line with $\Gamma=0$.

To confirm that the classical analysis is consistent with our ED calculations, we use the spin coherent states again to extract the ordered moment direction of the ED ground states in these stripe phases. For brevity, we here only construct cluster spin coherent state based on the stripe-$x$ and present the resulting probability maps in Fig.~\ref{fig:Proabilities}(c) and (d) for stripe-A and stripe-C, respectively. We can see that there are large overlaps between the exact cluster GS and stripe cluster spin coherent state, which indicates that the results based on the ED calculation is consistent with the classical analysis.
